Backward Population Synthesis: Mapping the Evolutionary History of Gravitational-Wave Progenitors

### 2022-06-07 src/tex/ms.tex
bug fix

We apply the method described in section \ref{sec:method} to the first GW event GW150914 \citep{GW150914}.
We use the \texttt{Overall_posterior} posterior samples for GW150914,
publicly available from the Gravitational wave Open Science Center \citep{LIGOScientific:2019lzm}. 
The parameters involved in the analysis and the range we allow for the inference are tabulated in table \ref{tab:parameters}.
The spin of BHs formed in isolated binaries depends strongly on the angular
momentum transport in massive stars which is still highly uncertain (see however \citet{Fuller2019, Bavera2020}),
therefore we only consider the two component masses in the observable space in both the
root-finding stage and the MCMC stage. For progenitor parameters, we characterize each guess with
five parameters: the two component masses $M_{\rm 1,ZAMS}$ and $M_{\rm 2,ZAMS}$, the orbital period $t_{\rm orb}$,
the eccentricity $e$, and the metallicity $Z$ at ZAMS. Note that the progenitor formation redshift is not
obtained through the root-finding process because the formation redshift does not intrinsically affect
the evolution of the binary. Instead, we compute the time it takes for the binary to evolve from
formation to the merger and add this time to the lookback time when a GW event is observed and limit the total
time to merger to be less than $13.7\,\rm{Gyr}$.
Using the total lookback time, we can compute the redshift of the binary at ZAMS formation following the
Planck 2018 cosmological model \citep{Planck2018}.
The main benefit of post-processing the redshift in this way is that we do not rely on a particular assumption
of star formation rate (SFR) distribution when we solve for the posterior distribution in redshift.
This means we can put the prior on formation redshift (or in general, metallicity-redshfit distribution) in
by reweighting the posterior distribution according to a particular SFR model,
and therefore do not have to rerun the inference every time we change the SFR model. This is especially helpful
since SFR models are still highly uncertain but strongly impact the local merger rates of BBHs \citep[e.g. ][]{Broekgaarden2021}.
For hyperparameters, we choose parameters that strongly affect
binary evolution in \texttt{COSMIC} for massive stars, including the common envelope
efficiency $\alpha$, the fraction of mass accreted onto the accretor during stable mass transfer $f_{\rm acc}$,
the critical mass ratio which determines whether Roche-overflow mass transfer
proceeds stably or produces a common envelope when the donor star is on the Hertzsprung gap
$q_{\rm crit,3}$, and the root-mean-square of the Maxwellian distribution
employed for CO natal kicks, $\sigma$. For systems which begin a common envelope 
with a Hertzsprung-gap donor, we always assume the pessimistic outcome that the two 
stars merge since the donor has likely not formed a strong core-envelope boundary 
\citep{Ivanova2004, Belczynski2008}.

@@

% Paragraph discussing the potential application on the population side.
To illustrate the potential benefit of using our method on the population level,
we perform the same analysis for all events in GWTC-3.
For events announced in GWTC-1, we use \texttt{Overall_posterior}, \texttt{PublicationSamples},\texttt{IMRPhenomXPHM_comoving} and \texttt{C01:Mixed} posterior samples, respectively.
All the data are publicly available from the Gravitational wave Open Science Center \citep{LIGOScientific:2019lzm}.
Plotted in figure
\ref{fig:GWTC-3_f_acc_mass} is the posterior density in the $m_{1,{\rm
GW}}-f_{\rm acc}$ space for most of the events in GWTC-3.
Each contour represents
the $68\%$ credible interval of the posterior density for that particular event.
There is a suggestive trend showing that $f_{\rm acc}$ could increase as the mass of
the progenitor increases. Such a trend implies the stable mass transfer
phase of a less massive binary would be preferentially non-conservative, with
more conservative mass transfer in more massive binary systems.

>>>>

We apply the method described in section \ref{sec:method} to the first GW event GW150914 \citep{GW150914}.
We use the \texttt{Overall\_posterior} posterior samples for GW150914,
publicly available from the Gravitational wave Open Science Center \citep{LIGOScientific:2019lzm}. 
The parameters involved in the analysis and the range we allow for the inference are tabulated in table \ref{tab:parameters}.
The spin of BHs formed in isolated binaries depends strongly on the angular
momentum transport in massive stars which is still highly uncertain (see however \citet{Fuller2019, Bavera2020}),
therefore we only consider the two component masses in the observable space in both the
root-finding stage and the MCMC stage. For progenitor parameters, we characterize each guess with
five parameters: the two component masses $M_{\rm 1,ZAMS}$ and $M_{\rm 2,ZAMS}$, the orbital period $t_{\rm orb}$,
the eccentricity $e$, and the metallicity $Z$ at ZAMS. Note that the progenitor formation redshift is not
obtained through the root-finding process because the formation redshift does not intrinsically affect
the evolution of the binary. Instead, we compute the time it takes for the binary to evolve from
formation to the merger and add this time to the lookback time when a GW event is observed and limit the total
time to merger to be less than $13.7\,\rm{Gyr}$.
Using the total lookback time, we can compute the redshift of the binary at ZAMS formation following the
Planck 2018 cosmological model \citep{Planck2018}.
The main benefit of post-processing the redshift in this way is that we do not rely on a particular assumption
of star formation rate (SFR) distribution when we solve for the posterior distribution in redshift.
This means we can put the prior on formation redshift (or in general, metallicity-redshfit distribution) in
by reweighting the posterior distribution according to a particular SFR model,
and therefore do not have to rerun the inference every time we change the SFR model. This is especially helpful
since SFR models are still highly uncertain but strongly impact the local merger rates of BBHs \citep[e.g. ][]{Broekgaarden2021}.
For hyperparameters, we choose parameters that strongly affect
binary evolution in \texttt{COSMIC} for massive stars, including the common envelope
efficiency $\alpha$, the fraction of mass accreted onto the accretor during stable mass transfer $f_{\rm acc}$,
the critical mass ratio which determines whether Roche-overflow mass transfer
proceeds stably or produces a common envelope when the donor star is on the Hertzsprung gap
$q_{\rm crit,3}$, and the root-mean-square of the Maxwellian distribution
employed for CO natal kicks, $\sigma$. For systems which begin a common envelope 
with a Hertzsprung-gap donor, we always assume the pessimistic outcome that the two 
stars merge since the donor has likely not formed a strong core-envelope boundary 
\citep{Ivanova2004, Belczynski2008}.

@@

% Paragraph discussing the potential application on the population side.
To illustrate the potential benefit of using our method on the population level,
we perform the same analysis for all events in GWTC-3.
For events announced in GWTC-1, we use \texttt{Overall\_posterior}, \texttt{PublicationSamples},\texttt{IMRPhenomXPHM\_comoving} and \texttt{C01:Mixed} posterior samples, respectively.
All the data are publicly available from the Gravitational wave Open Science Center \citep{LIGOScientific:2019lzm}.
Plotted in figure
\ref{fig:GWTC-3_f_acc_mass} is the posterior density in the $m_{1,{\rm
GW}}-f_{\rm acc}$ space for most of the events in GWTC-3.
Each contour represents
the $68\%$ credible interval of the posterior density for that particular event.
There is a suggestive trend showing that $f_{\rm acc}$ could increase as the mass of
the progenitor increases. Such a trend implies the stable mass transfer
phase of a less massive binary would be preferentially non-conservative, with
more conservative mass transfer in more massive binary systems.
